---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```
## Overview

<!-- badges: start -->
<!-- badges: end -->

Multiple Hidden Markov Model Regression (HMMR) for the **segmentation** of multivariate time series with regime changes.

The model assumes that the time series is governed by a sequence of hidden discrete regimes/states, where each regime/state has multivariate Gaussian regressors emission densities. The model parameters are estimated by MLE via the EM algorithm.

## Installation

You can install the development version of MHMMR from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/MHMMR")
```

To build *vignettes* for examples of usage, type the command below instead:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/MHMMR", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         build_vignettes = TRUE)
```

Use the following command to display vignettes:

```{r, eval = FALSE}
browseVignettes("MHMMR")
```

## Usage

```{r, message = FALSE}
library(MHMMR)

data("simulatedtimeseries")

K <- 5 # Number of regimes (states)
p <- 3 # Dimension of beta (order of the polynomial regressors)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

n_tries <- 1
max_iter <- 1500
threshold <- 1e-6
verbose <- TRUE

mhmmr <- emMHMMR(simulatedtimeseries$X, simulatedtimeseries[, 2:ncol(simulatedtimeseries)],
                 K, p, variance_type, n_tries, max_iter, threshold, verbose)

mhmmr$plot()
```
